---
title: "SensAnalyzR_Intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SensAnalyzR_Intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(knitr)
```

# Overview of SensAnalyzR - How to Guide
## A Sensitivity Analysis Tool

This code was built with 6 distinct inputs to be used. Yeah, it's alot of inputs, however it allows for a greater adaptability depending on the problem.  

The way the tool is designed if for market baskets within datasets.

Before we get too far in here are the packages you will need.

### Packages to call
```{r }
library(dplyr)
library(plyr)
library(purrr)
library(tidyr)
library(tibble)

library(SensAnalyzR)
```

The main inputs are as follows; this example uses the mtcars dataset.

### Inputs Setup

```{r}

#The dataset you want to analyze
data<-mtcars
#The good in your market basket
goods<-c("hp","gear","wt")
#The weights you want to give the items in your market basket
weight<-c(6,7,8)
#The column of the dataset you want to disaggregate by
disagg<-"cyl"
#The percentages you want to assess
percent<-c(.05,.1,.15)
#The function you want to summarize by in the disaggregation
func<-median
```
I WOULD SERIOUSLY CONSIDER JUST COPYING THESE LINES INTO YOUR CODE THEN CHANGING AS NEEDED.


### Explaination

More explaination on the way these interact. 

Data-your dataset, please make sure it has the column corresponding to what is in your goods and disagg arguments

Goods-a group of goods you want included in your market basket, should be column names within the dataset.

Weight-the appropriate weights you want to give to the goods within the market basket. (THIS NEEDS TO BE THE SAME LENGTH LIST AS THE GOODS).

Disagg-should be column within the dataset, do not make this a column within your goods list.

Percent-the percents you would like to be multiplied along each column. In the example c(.05,.1,.15) corresponds to 5%,10%,15%. Also the function makes all percentages negatives as well so the output for c(.05,.07) would be 5%,7%,0%,-5%,-7%.

Func-the function you would like summarized by during the disaggregation. I would recommend median or mean.

### Actually Running Code

```{r}
output<-sens_analysis(data, goods, weight, disagg, percent, func)
```
Or

```{r}

output_other<-(sens_analysis(mtcars, c("hp","gear","wt"), c(1,2,3), "cyl", c(.03,.08), median))
```

Produces an object output

### Example Data Output
As from the first example in the part of the R code I said you should copy


|type|cyl|hp|gear|wt|total|
|----|---|--|----|--|-----|
| hp BY 0% OVER cyl|	4	|91.00|	8.0|	6.600|	105.60|
|	hp BY 0% OVER cyl|	6	|110.00|	8.0|	9.645|	127.64|
|	hp BY 0% OVER cyl|	8	|192.50|	6.0|	11.265|	209.76|
|	hp BY 5% OVER cyl|	4	|95.55|	8.0|	6.600|	110.15|
|	hp BY 5% OVER cyl|	6	|115.50|	8.0|	9.645|	133.15|
|	hp BY 5% OVER cyl|	8 |202.12|	6.0|	11.265|	219.38|
|	hp BY 10% OVER cyl|	4	|100.10|	8.0|	6.600|	114.70|
|	hp BY 10% OVER cyl|	6	|121.00|	8.0|	9.645|	138.65|
|	hp BY 10% OVER cyl|	8	|211.75|	6.0|	11.265|	229.01|
| hp BY 15% OVER cyl|	4	|104.65|	8.0|	6.600|	119.25|
|	hp BY 15% OVER cyl|	6	|126.50|	8.0|	9.645|	144.15|
|	hp BY 15% OVER cyl|	8	|221.37|	6.0|	11.265|	238.63|
|	hp BY -5% OVER cyl|	4	|86.45|	8.0|	6.600|	101.05|
|	hp BY -5% OVER cyl|	6	|104.50|	8.0|	9.645|	122.14|
|	hp BY -5% OVER cyl|	8	|182.88|	6.0|	11.265|	200.14|

As you can see the "by 0%" is just the normal no percent option. From there all the percentages are multiplied by the column they indicate and a new total is formed.



